---
title: "regshape Package Vignette"
author: "Stephen Ramsey and Jichen Yang"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{regshape Package Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

The regshape R package provides a classifier for predicting whether a given oligonucleotide sequence (of 
length *l* bp, where *l* would typically vary from six to as high as 25 bp) is, or is not, a transcription factor (TF) binding site. It should be noted that regshape does not predict whether a give sequence is or
is not a binding site for a specific type of transcription factor; it is a TF-generic classifier for 
regulatory elements based on local three-dimensional shape properties of the DNA as can be discerned from the nucleotide sequence. The regshape package uses the Random Forest classifier (provided by the 
randomForest R package) and it is based on a compendium of representative TF binding site sequences from the JASPAR database (release 5.0) and on a large representative sample of human noncoding DNA sequence from which known TF binding sites (from ENCODE ChIP-seq genome location datasets from 457 different experiments 
comprising 119 different TFs). The regshape package is available on GitHub at the URL 
<a href="http://github.com/ramseylab/regshape">github.com/ramseylab/regshape</a>. The regshape package is furnished under the GNU General Public License version 2.0 (see LICENSE file in the package distribution). There are two ways to use the regshape package; processing a vector of short sequences (each of length *l*), or processing a single long sequence using a sliding window of length *l*.

To use regshape, the package library must first be loaded into your R session:

```{r}
library(regshape)
```

Once the regshape package has been loaded, you are ready to compute shape scores for a vector of
short DNA sequences (in this example, *l*=6 but any value greater than six is allowed):

```{r}
getShapeScores(c("AAAAAA","GATACG","TCGAGT"))
```

In many situations, it is convenient to obtain shape scores for short length-*l* subsequences of a long
DNA sequence. For this example, we will use *l*=8:

```{r}
getShapeScoresSlidingWindow("AGACACGACGTCGATCATAAACTAGATCAGCCTGA", 8)
```
